## shoRtcut

shoRtcut is an R package to make the life with R even more easier.

### Installation

You can install `shoRcut` from `github` using the `devtools` package.

```{r, message=FALSE, echo=FALSE, warning=FALSE}
file.rename("README.md", "../README.md")
rm(list=ls())
```



```{r, message=FALSE}
library(devtools)
install_github("shoRtcut", "jbkunst")
library(shoRtcut)
```




### Some functions

#### Frequency table

The function `freqtable` return a `data.frame` with the information of the counts of the levels of variable.

```{r}
data(credit)
freqtable(credit$marital_status)
freqtable(credit$marital_status, add.total=FALSE)
freqtable(credit$residence_type, sort.by.count=TRUE, pretty=TRUE)
```

This function also make a cross table if `variable2` argument is given.

```{r}
freqtable(credit$marital_status, credit$residence_type)
freqtable(credit$marital_status, credit$residence_type,
          add.total=FALSE, pretty=TRUE)
```


#### Exporting tables

The function `writetable` requirev the name (with path if you want) of the file with the extension and the `data.frame` to export. 

```{r, message=FALSE}
data(cars)

t1 <- cbind(head(cars, 3), var1 = "excel")
t2 <- cbind(tail(cars, 3), var2 = "text")

writetable(t1, "excel_file.xlsx")
writetable(t2, "txt_file.txt")
```

#### Reading tables

The function `readtable` require the names of files to read. You can read simoultaneus files. This function not necessary require all tables with the same number columns because use the `rbind.fill` function in the `plyr` package.


```{r message=FALSE, }
table <- readtable(c("excel_file.xlsx", "txt_file.txt"))
```
```{r}
table
```
