## shoRtcut

shoRtcut is an R package to make the life with R even more easier.

### Installation

You can install `shoRcut` from `github` using the `devtools` package.

```{r, message=FALSE, echo=FALSE, warning=FALSE}
d <- readLines("README.md")
d <- gsub("\\(figure\\/", "\\(readme\\/figure\\/", d)
writeLines(d, "../README.md")
rm(list=ls())
```



```{r, message=FALSE}
library(devtools)
install_github("shoRtcut", "jbkunst")
library(shoRtcut)
```




### Some functions

#### Frequency table

The function `freqtable` return a `data.frame` with the information of the counts of the levels of variable.

```{r}
data(credit)
freqtable(credit$marital_status)
freqtable(credit$marital_status, add.total=FALSE)
freqtable(credit$residence_type, sort.by.count=TRUE, pretty=TRUE)
```

This function also make a cross table if `variable2` argument is given.

```{r}
freqtable(credit$marital_status, credit$residence_type)
freqtable(credit$marital_status, credit$residence_type,
          add.total=FALSE, pretty=TRUE)
```


#### Exporting tables

The function `writetable` requires the name (reltavie or full path) of the file with the extension and the `data.frame` to export. Also support `json` format.

```{r, message=FALSE}
data(iris)

t1 <- cbind(head(iris, 3), from = "excel")
t2 <- cbind(tail(iris, 3), from = "text")
t3 <- cbind(head(iris, 3), other_from = "json")

writetable(t1, "excel_file.xlsx")
writetable(t2, "txt_file.txt")
writetable(t3, "json_file.json")
```


```{r, message=FALSE}
data(mtcars)
writetable(mtcars, "file.json")
```

#### Reading tables

The function `readtable` require the names of files to read. You can read simoultaneus files. This function not necessary require all tables with the same number columns because use the `rbind.fill` function in the `plyr` package.


```{r message=FALSE, }
table <- readtable(files=c("excel_file.xlsx", "txt_file.txt"))
table <- readtable(files=c("json_file.json"))
table
```

#### Plot functions

There are shortcuts functions to plot distributions of variables based on `ggplot2` package.

```{r message=FALSE, fig.height=5, fig.width=5}
data(credit)
plot_bar(credit$marital_status)
```

```{r message=FALSE, fig.height=5, fig.width=5}
plot_hist(credit$age) + ggtitle("A title") + xlab("I'm here, in the xlab")
```

```{r message=FALSE, fig.height=5, fig.width=5}
plot_density(credit$payment_day, color="darkred") 
```

#### Other functions
There are other functions and others in development:
* str_capitalize
* str_clean
* str_first_upper
* str_is_email
* str_pattern
* truncate
* plot_pie
* plot_pareto
