## shoRtcut

shoRtcut is an R package to make the life with R even more easier.

### Installation

You can install `shoRcut` from `github` using the `devtools` package.

```{r, message=FALSE, echo=FALSE}
file.rename("README.md", "../README.md")
```



```{r, message=FALSE}
library(devtools)
install_github("shoRtcut", "jbkunst")
library(shoRtcut)
```




### Some functions

#### Frequency table

The function `freqtable` return a `data.frame` with the information of the counts of the levels of variable.

```{r}
data(iris)
freqtable(iris$Species)
freqtable(iris$Species, add.total=FALSE)
```


#### Exporting tables

The function `writetable` require only the name of the file with the extension. 


```{r, message=FALSE}
data(cars)

t1 <- cbind(head(cars, 3), var1 = "excel")
t2 <- cbind(tail(cars, 3), var2 = "text")

writetable(t1, "excel_file.xlsx")
writetable(t2, "txt_file.txt")
```

#### Reading tables

The function `readtable` require the names of files (always with extension) to read. You can read simoultaneus files.  This function not necessary require all tables with the same number columns.


```{r message=FALSE, }
table <- readtable(c("excel_file.xlsx", "txt_file.txt"))
```
```{r}
table
```
